First, load dataset and clean data as necessary.

```{r}
## read and create subsets
cope_subset <- read_csv("data/cope_subset.csv")
cope_subset %>% datatable(
  rownames = FALSE,
  options = list(
    pageLength = 5,
    columnDefs = list(list(className = 'dt-center', 
                      targets = 0:4))))

## gender identity subset
dem_gender_subset <- cope_subset %>% dplyr::select(starts_with("b_dem_gender"))

## coping strategies

dem_cope_subset <- cope_subset %>% dplyr::select(starts_with("b_covid_cope"))

## family challenges

dem_family_subset <- cope_subset %>% dplyr::select(starts_with("b_covid_family"))

## race

dem_race_subset <- cope_subset %>% dplyr::select(starts_with("b_dem_race"))

## sexual orientation

dem_orient_subset <- cope_subset %>% dplyr::select(b_dem_orientation)

## coping strategy subset
dem_cope_subset <- dem_cope_subset %>%
  dplyr::select(-"b_covid_cope_1_including_talking_with_people_you_trust_about_your_concerns_and_how_you_are_feeling")



```


## Collapse categories

Re-code `sexual orientation`, `race`, `family challenge` variables by collapsing some categories with limited number of samples, and generating composite categories.

#### Recode sexual orientation
```{r sex orient}
## recode sexual orientation
recode_orient_dat <- dem_orient_subset %>%
mutate(recod_orient= case_when(
  b_dem_orientation %in% c("Asexual", "I do not use a label", "Other/Not listed (please specify)") ~ "Other",
  b_dem_orientation %in% c("Gay/Lesbian/Homosexual", "Queer", "Unsure/Questioning") ~ "LGBTQ",
  b_dem_orientation %in% c("Bisexual", "Pansexual") ~ "LGBTQ",
  b_dem_orientation == "Heterosexual/Straight" ~ "Heterosexual",
  TRUE ~ b_dem_orientation
))
```

#### Recode family challenges
```{r}
## recode family challenge
### number of challenges
challenge_num_dat <- dem_family_subset %>%
  mutate(challenge_num = apply(., 1, sum)) %>%
  mutate(challenge_num = ifelse(b_covid_family_the_covid_19_pandemic_has_not_affected_me_or_my_family_in_these_ways_in_the_past_2_weeks=="1",0,challenge_num)) %>%
  mutate(challenge_num3 = ifelse(challenge_num>=2, 2, challenge_num))

### category of challenges
challenge_cat_dat <-  dem_family_subset %>%
  mutate(challenge_cat = case_when(
    b_covid_family_family_did_not_enough_enough_money_for_food == 1 |
      b_covid_family_family_did_not_have_enough_money_for_gas_transportation == 1 |
      b_covid_family_family_did_not_have_a_regular_place_to_sleep_or_stay==1 |
      b_covid_family_family_did_not_have_enough_money_to_pay_rent == 1 ~ "Financial",

    b_covid_family_i_could_not_attend_school_in_person == 1 |
      b_covid_family_i_could_not_attend_school_at_all == 1 ~ "School",

    b_covid_family_other == 1 ~ "Other",

    b_covid_family_the_covid_19_pandemic_has_not_affected_me_or_my_family_in_these_ways_in_the_past_2_weeks == 1 ~ "No impact",

    TRUE ~ "No"
  ))


challenge_cat_dat <- dem_family_subset %>%
  mutate(
    Financial = b_covid_family_family_did_not_enough_enough_money_for_food == 1 |
      b_covid_family_family_did_not_have_enough_money_for_gas_transportation == 1 |
      b_covid_family_family_did_not_have_a_regular_place_to_sleep_or_stay == 1 |
      b_covid_family_family_did_not_have_enough_money_to_pay_rent == 1,

    School = b_covid_family_i_could_not_attend_school_in_person == 1 |
      b_covid_family_i_could_not_attend_school_at_all == 1,

    Other = b_covid_family_other == 1,

    No_impact = b_covid_family_the_covid_19_pandemic_has_not_affected_me_or_my_family_in_these_ways_in_the_past_2_weeks == 1,

    challenge_cat = case_when(
      Financial & School & Other ~ "Other",
      Financial & School ~ "Other",
      Financial & Other ~ "Other",
      School & Other ~ "Other",
      Financial ~ "Other",
      School ~ "School",
      Other ~ "Other",
      No_impact ~ "No impact",
      TRUE ~ "No challenge"
    )
  ) %>%
  dplyr::select(-Financial, -School, -Other, -No_impact)



```

#### Recode race
```{r}
## identify all race patterns
race_pattern_dat <- cope_subset %>%
  dplyr::select(starts_with("b_dem_race")) %>%
  mutate(race_pattern = apply(., 1, function(row) paste0(row, collapse = "")))

cope_subset1 <- cope_subset %>%
  mutate(race_pattern =race_pattern_dat$race_pattern ) %>%
  ## recode race
  mutate(recode_race = case_when(
    race_pattern == "000010" ~ 'White',
    race_pattern == "000001" ~ 'Black/African-American',
    race_pattern == "010000" ~ 'Asian Including Asian Desi',
    race_pattern == "001000" ~ 'Hispanic/Latinx',
    race_pattern == "000000" ~ 'Prefer not to answer',
    TRUE ~ 'Mixed'
  )) %>%
  ## recode sexual orientation
  mutate(recode_orient = recode_orient_dat$recod_orient) %>% 
  
  dplyr::select(-race_pattern) %>%
  ## recode language
  mutate(recode_language = case_when(
    b_dem_language == "English" ~ 'English',
    TRUE ~ 'Other'
  )) %>%
  ## reorder variables
  dplyr::select(-b_dem_language,-starts_with("b_dem_race")) %>%
  dplyr::select(recode_race,starts_with("b_dem_gender"),b_screener_age,b_dem_sex,b_dem_orientation,
         starts_with("b_covid_family"), starts_with("b_covid_cope"),recode_language, everything()
         )
```

## Latent Class Analysis(LCA)

Apply LCA to find the latent class variables for `gender identity` and `coping strategies`, respectively.

### Gender identity

```{r results='hide'}
## Gender identity
tmp <- dem_gender_subset%>%
  mutate(gender_pattern = apply(., 1, function(row) paste0(row, collapse = "")))

## check patterns
tmp1 <- tmp$gender_pattern %>% table() %>% data.frame()

genderid_dat <- dem_gender_subset

## check correlation
genderid_dat_cor <- cor(genderid_dat) %>% data.frame


# The transgender indicator and gender_expansive indicator variables are removed because these two variables are the 
# composite variables of other indicators


### correlation matrix 
#genderid_dat_cor_melted <- melt(as.matrix(genderid_dat_cor))


# ggplot(data = genderid_dat_cor_melted, aes(x=Var1, y=Var2, fill=value)) +
#   geom_tile(color = "white") +
#   scale_fill_gradient2(low = "blue", high = "red", mid = "white",
#                        midpoint = 0, limit = c(-1, 1), space = "Lab",
#                        name="Correlation") +
#   theme_minimal() +
#   theme(axis.text.x = element_text(angle = 45, vjust = 1,
#                                    size = 12, hjust = 1)) +
#   coord_fixed() +
#   labs(x = "", y = "") +
#   ggtitle("Correlation Matrix Heatmap")

## prepare input data for poLCA

## only accept indicator variables coded start from 1 (transfer 01 --> 12)
recode_variables <- function(df) {
  df <- df %>% mutate(across(everything(), ~ as.integer(as.factor(.))))
  return(df)
}


## input of the poLCA
genderid_dat_LCA <- genderid_dat %>%
  recode_variables() %>%
  rename_with(~ str_remove(., "b_dem_gender_"), starts_with("b_dem_gender_"))

## define the indicator variables of LCA model
f1 <- cbind(
  agender, not_sure, other_please_specify,
  androgynous, nonbinary, two_spirited,
  female_to_male_transgender_ftm, trans_female_trans_feminine,
  trans_male_trans_masculine,
  # gender_expansive, ## composite removed
  third_gender, genderqueer, male_to_female_transgender_mtf,
  man_boy,
  # transgender, ## composite removed
  woman_girl) ~ 1

set.seed(1017)
gender_LCA2 <- poLCA(f1, data = genderid_dat_LCA,
              nclass = 2)


gender_LCA3 <- poLCA(f1, data = genderid_dat_LCA,
              nclass = 3)

gender_LCA4 <- poLCA(f1, data = genderid_dat_LCA,
              nclass = 4)


gender_LCA5 <- poLCA(f1, data = genderid_dat_LCA,
              nclass = 5)


gender_models <- list(gender_LCA2, gender_LCA3, gender_LCA4, gender_LCA5)
gender_model_stats <- data.frame(
  Model = 2:5,
  G2 = sapply(gender_models, function(x) x$Gsq),
  AIC = sapply(gender_models, function(x) x$aic),
  BIC = sapply(gender_models, function(x) x$bic)
)
```

#### Step 1: LCA model selection
Compare LCA models for different number of classes.

the LCA model with 3 latent classes has comparable $G^2$, AIC, BIC. (could also use scree plot). therefore, a model with **3 latent class** is selected for gender identity. 
```{r}
kable(gender_model_stats, caption = "Model Comparison for Different Number of Classes (Gender Identity variable)")
```


#### Step 2: classification error: averaged posterior probability(APP)
print APP, results suggest low classification error(APP>0.7).
```{r}
posterior_probs <- gender_LCA3$posterior

assigned_class <- apply(posterior_probs, 1, which.max)

mean_posterior_by_class <- numeric(ncol(posterior_probs))

for (k in 1:ncol(posterior_probs)) {
  mean_posterior_by_class[k] <- mean(posterior_probs[assigned_class == k, k])
}

print(mean_posterior_by_class)
```

#### Step 3: Final latent class probabilities

The probability of belonging to a specific class is calculated for each individual, and each individual is classified to a specific class based on the max. posterior probability. Below is the results of the posterior probabilities for all subjects (prob. of being in class $j$).
```{r}
## get predicted class (gender identity)
genderid_class <- gender_LCA3$predclass
genderid_predprob <- gender_LCA3$posterior
colnames(genderid_predprob) <- paste0("Class",c(1:3))
genderid_predprob %>% datatable(
  rownames = FALSE,
  options = list(
     pageLength = 5,
    columnDefs = list(list(className = 'dt-center', 
                      targets = 0:2))))
```
#### Step 4: Assign label to each latent class (gener identity)
Visualize the probabilities of answering yes of each item by latent class (Pr(individual answers yes to an item $|$ in class $j$)) to understand the underlying pattern.
```{r genderid_plot, fig.height=6, fig.width=6, message=FALSE, warning=FALSE}
# probabilities of answering yes by class
probs_list <- gender_LCA3$probs

probs_df <- do.call(rbind, lapply(names(probs_list), function(var) {
  prob_df <- as.data.frame(probs_list[[var]])
  prob_df$variable <- var
  prob_df$class <- rownames(prob_df)
  prob_df
})) %>% dplyr::select(-`Pr(1)`)

probs_df_list <- list()


for (var in names(probs_list)) {
  prob_df <- as.data.frame(probs_list[[var]])
  prob_df$variable <- var
  prob_df$class <- rownames(prob_df)
  probs_df_list[[var]] <- prob_df
}


probs_df_combined <- bind_rows(probs_df_list)%>%
  dplyr::select(-`Pr(1)`) %>% 
  mutate(variable = dplyr::recode(variable,
    "agender" = "agender",
    "not_sure" = "not sure",
    "other_please_specify" = "other",
    "androgynous" = "androgynous",
    "nonbinary" = "nonbinary",
    "two_spirited" = "two spirited",
    "female_to_male_transgender_ftm" = "female to male",
    "trans_female_trans_feminine" = "female trans feminine",
    "trans_male_trans_masculine" = "male trans masculine",
    "third_gender" = "third gender",
    "genderqueer" = "genderqueer",
    "male_to_female_transgender_mtf" = "male to female",
    "man_boy" = "man/boy",
    "woman_girl" = "woman/girl"
  )) %>% 
   mutate(class = dplyr::recode(class,
                                "class 1: " = "Class 1: Non-binary",
                                "class 2: " = "Class 2: Women/girls",
                                "class 3: " = "Class 3: Male/Masculine")
   ) %>% 
  group_by(variable) %>% 
  mutate(maxprob = max(`Pr(2)`)) %>%
  ungroup() %>% 
  mutate(maxprob = ifelse(maxprob==`Pr(2)`,maxprob,NA) %>% round(2),
         maxprob = ifelse(maxprob %in% c(0.01,0.02,0.03,0.12,0.23,0.2,0.19,0.09,0.38),NA,maxprob)
         )

## the condit. prob
gender_prob_plot <- ggplot(probs_df_combined, aes(x = variable, y = `Pr(2)`, color = class, group = class)) +
  geom_line(size = 1) + 
  geom_point(size = 1.5)+
  geom_text(aes(label = round(maxprob, 2)), vjust = -1, size = 3, show.legend = FALSE) +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 12)) +  
  labs(x = "", y = "Probability of answering yes ") +
   ggtitle("(A) Latent classes for gender identity")+
  scale_color_brewer(palette = "Set1") +  
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12, face = "bold"),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.x = element_blank(),  
    panel.grid.minor.x = element_blank() 
  )

gender_prob_plot

ggsave("figures/gender_prob_plot.png", width = 6, height = 6, dpi = 600)
```


### Coping strategies

#### Step 1: LCA model selection
Build and compare LCA models
```{r copeLCA, results='hide'}
cope_dat_LCA <- dem_cope_subset %>%
  recode_variables() %>%
  rename_with(~ str_remove(., "b_covid_cope_1_"), starts_with("b_covid_cope_1_"))


f2 <- cbind(connecting_with_others, contacting_a_healthcare_provider,
        drinking_alcohol, smoking_more_cigarettes_or_vaping_more) ~ 1

set.seed(1017)
cope_LCA2 <- poLCA(f2, data = cope_dat_LCA,
              nclass = 2)
cope_LCA3 <- poLCA(f2, data = cope_dat_LCA,
              nclass = 3)

cope_LCA4 <- poLCA(f2, data = cope_dat_LCA,
              nclass = 4)
cope_LCA5 <- poLCA(f2, data = cope_dat_LCA,
              nclass = 5)

cope_models <- list(cope_LCA2, cope_LCA3, cope_LCA4, cope_LCA5)
cope_model_stats <- data.frame(
  Model = 2:5,
  G2 = sapply(cope_models, function(x) x$Gsq),
  AIC = sapply(cope_models, function(x) x$aic),
  BIC = sapply(cope_models, function(x) x$bic)
)
```

```{r}
kable(cope_model_stats, caption = "Model Comparison for Different Number of Classes (Coping strategy variable)")
```


#### Step 2: Classification error: averaged posterior probability(APP)
print averaged posterior probability(APP) for coping strategy, results suggest low classification error(APP>0.7).
```{r}
posterior_probs <- cope_LCA3$posterior

assigned_class <- apply(posterior_probs, 1, which.max)

mean_posterior_by_class <- numeric(ncol(posterior_probs))

for (k in 1:ncol(posterior_probs)) {
  mean_posterior_by_class[k] <- mean(posterior_probs[assigned_class == k, k])
}

print(mean_posterior_by_class)
```

#### Step 3: Final latent class probabilities
Similarly, get the predicted posterior probability of the latent variable for coping strategy.
```{r}
## get predicted class (gender identity)
cope_class <- cope_LCA3$predclass
cope_predprob <- cope_LCA3$posterior
colnames(cope_predprob) <- paste0("Class",c(1:3))
cope_predprob %>% datatable(
  rownames = FALSE,
  options = list(
     pageLength = 5,
    columnDefs = list(list(className = 'dt-center', 
                      targets = 0:2))))
```

#### Step 4: Assign label to each latent class (coping strategies)
```{r cope_plot, fig.height=6, fig.width=6, message=FALSE, warning=FALSE}
probs_list <- cope_LCA3$probs

probs_df <- do.call(rbind, lapply(names(probs_list), function(var) {
  prob_df <- as.data.frame(probs_list[[var]])
  prob_df$variable <- var
  prob_df$class <- rownames(prob_df)
  prob_df
})) %>% dplyr::select(-`Pr(1)`)

probs_df_list <- list()

for (var in names(probs_list)) {
  prob_df <- as.data.frame(probs_list[[var]])
  prob_df$variable <- var
  prob_df$class <- rownames(prob_df)
  probs_df_list[[var]] <- prob_df
}


probs_df_combined <- bind_rows(probs_df_list)%>%
  dplyr::select(-`Pr(1)`) %>% 
   mutate(variable = dplyr::recode(variable,
    "connecting_with_others" = "connect with others",
                      "contacting_a_healthcare_provider" = "contact healthcare provider",
                      "drinking_alcohol" = "drink alcohol",
                      "smoking_more_cigarettes_or_vaping_more" = "smoke/vape more")) %>% 
   mutate(class = dplyr::recode(class,
                                "class 3: " = "Class 3: Positive ",
                                "class 2: " = "Class 2: No action",
                                "class 1: " = "Class 1: Combined")
   ) %>% 
  group_by(variable) %>% 
  mutate(maxprob = max(`Pr(2)`)) %>%
  ungroup() %>% 
  mutate(maxprob = ifelse(maxprob==`Pr(2)`,maxprob,NA) %>% round(2),
         maxprob = ifelse(maxprob==0.16,NA,maxprob))

cope_prob_plot <- ggplot(probs_df_combined, aes(x = variable, y = `Pr(2)`, color = class, group = class)) +
  geom_line(size = 1) + 
  geom_point(size = 1.5)+
  geom_text(aes(label = round(maxprob, 2)), vjust = -1, size = 3, show.legend = FALSE) +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 12)) + 
  labs(x = "", y = "Probability of answering yes ") +
   ggtitle("(B) Latent classes for coping strategies")+
  scale_color_brewer(palette = "Set1") +  
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12, face = "bold"),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.x = element_blank(),  
    panel.grid.minor.x = element_blank() 
  )

cope_prob_plot

ggsave("figures/cope_prob_plot.png", width = 6, height = 6, dpi = 600)

```

```{r message=FALSE, warning=FALSE, include=FALSE}
## for report
LCA_plots <- ggarrange(gender_prob_plot, cope_prob_plot, ncol = 2, nrow = 1)

ggsave("figures/LCA_plots.png", width = 10, height = 7, dpi = 600)
```

## Missing values

98.6% of the subjects have complete information. 

```{r}
miss_dat <- cope_subset1 %>%

  mutate(across(starts_with("recode_race"), ~ ifelse(. == "Prefer not to answer", NA, .))) %>%

  mutate(b_dem_sex = ifelse(b_dem_sex %in% c("Prefer not to say", "Other"), NA, b_dem_sex)) %>%
  
  mutate(across(starts_with("recode_orient"), ~ ifelse(. == "I do not want to respond", NA, .)))%>% dplyr::select(b_dem_sex,recode_orient,recode_race)

colnames(miss_dat) <- c("Biological sex","Sexual orientation","Race")

vis_miss(miss_dat)



```

Tabulate the number and percentage of missing. The missing rate is low, so complete case analysis will be used later.

```{r miss_plot,fig.height=6, fig.width=6,message=TRUE, warning=FALSE}
missing_summary <- miss_var_summary(miss_dat)

miss_plot <- ggplot(missing_summary, aes(x = reorder(variable, -n_miss), y = n_miss)) +
  geom_bar(stat = "identity", fill = "lightblue",size=0.1) +
  geom_text(aes(label = paste0(n_miss, " (", round(pct_miss, 2), "%)")), 
            hjust = 1,  vjust = 0.5, color = "black") +
  coord_flip() +
  theme_minimal() +
  labs( #title = "Missing Data by Variable",
       x = "Variable",
       y = "Missing Count (Percentage)") +
  theme(axis.text.y = element_text(size = 10),
        axis.title = element_text(size = 12),
        plot.title = element_text(size = 14, face = "bold")) +
 # coord_cartesian(ylim = c(0, 40))+
  theme_minimal()
miss_plot 
```

Check if there is any missing pattern among missing variables: No pattern presents!
```{r}
gg_miss_upset(miss_dat)
```

## The final working dataset

After some investigation, I decided to do a complete case analysis(CCA), the final working dataset is then generated. 

```r
dat_cc <- cope_subset3 %>% 
   filter(recode_race!="Prefer not to answer") %>%  ## 1468
  filter(b_dem_sex!="Prefer not to say" & b_dem_sex!="Other") %>% ## 1447
  filter(orientation!="I do not want to respond") ## 1441
```
```{r}
cope_subset2 <- cope_subset1 %>%

  mutate(across(starts_with("recode_race"), ~ ifelse(. == "Prefer not to answer", NA, .))) %>%

  mutate(b_dem_sex = ifelse(b_dem_sex %in% c("Prefer not to say", "Other"), NA, b_dem_sex)) %>%
  
  mutate(across(starts_with("recode_orient"), ~ ifelse(. == "I do not want to respond", NA, .)))

## use the latent variable genderid3 as a surragate for a series of gener identity related quesitons
cope_subset2$genderid3 <- genderid_class

## use the latent variable cope3 as a surragate for a series of coping strategies related quesitons
cope_subset2$cope3 <- cope_class

cope_subset3 <- cope_subset2 %>%
  mutate(family_num =challenge_num_dat$challenge_num3,
         family_cat = challenge_cat_dat$challenge_cat) %>%
  dplyr::select(c("b_response_id", "condition", "b_cdi_mean", "f1_cdi_mean", "recode_race",
           #"b_dem_gender_agender", "b_dem_gender_not_sure",
           #"b_dem_gender_other_please_specify", "b_dem_gender_androgynous",
           #"b_dem_gender_nonbinary", "b_dem_gender_two_spirited", "b_dem_gender_female_to_male_transgender_ftm",
           #"b_dem_gender_trans_female_trans_feminine", "b_dem_gender_trans_male_trans_masculine",
           #"b_dem_gender_gender_expansive", "b_dem_gender_third_gender",
           #"b_dem_gender_genderqueer", "b_dem_gender_male_to_female_transgender_mtf",
          # "b_dem_gender_man_boy", "b_dem_gender_transgender", "b_dem_gender_woman_girl",
           "b_screener_age", "b_dem_sex", "recode_orient",
            #"b_covid_family_family_did_not_enough_enough_money_for_food",
           #"b_covid_family_family_did_not_have_a_regular_place_to_sleep_or_stay",
           #"b_covid_family_i_could_not_attend_school_in_person", "b_covid_family_i_could_not_attend_school_at_all",
           #"b_covid_family_other", "b_covid_family_family_did_not_have_enough_money_for_gas_transportation",
           #"b_covid_family_family_did_not_have_enough_money_to_pay_rent",
           #"b_covid_family_the_covid_19_pandemic_has_not_affected_me_or_my_family_in_these_ways_in_the_past_2_weeks",
           #"b_covid_cope_1_connecting_with_others", "b_covid_cope_1_including_talking_with_people_you_trust_about_your_concerns_and_how_you_are_feeling",
           #"b_covid_cope_1_contacting_a_healthcare_provider", "b_covid_cope_1_drinking_alcohol",
           #"b_covid_cope_1_smoking_more_cigarettes_or_vaping_more",
           "recode_language",
           "genderid3","family_num","family_cat",
           # "family3",
          "cope3")) %>% 
  mutate(
   # condition = factor(condition),
    recode_race = factor(recode_race),
   # b_screener_age = factor(b_screener_age),
    b_dem_sex = factor(b_dem_sex),
    recode_orient = factor(recode_orient),
    genderid3 = factor(genderid3),
    family_num = factor(family_num),
    family_cat = factor(family_cat),
    cope3 = factor(cope3)
  )

dat_cc <- cope_subset3 %>% 
   filter(!is.na(recode_race)) %>%  ## 1468
  filter(!is.na(b_dem_sex)) %>% ## 1447
  filter(!is.na(recode_orient) )## 1441


dat_cc %>%  datatable(
  rownames = FALSE,
  options = list(
    pageLength = 5))

save(dat_cc,file="data/dat_cc.rds")
```

```{r}

table1_dat <- cope_subset3 %>% 

 mutate(genderid3 = dplyr::recode(genderid3,
                                "1" = "Non-binary",
                                "2" = "Women/girls",
                                "3" = "Male/Masculine")
   ) %>% 
     mutate(family_num = dplyr::recode(family_num,
                                "0" = "0",
                                "2" = ">=2",
                                "1" = "1")
   )  %>% 
  mutate(cope3 = dplyr::recode(cope3,
                                "3" = "Positive",
                                "2" = "No action",
                                "1" = "Combined")
   )  %>% 
   filter(!is.na(recode_race)) %>%  ## 1468
  filter(!is.na(b_dem_sex)) %>% ## 1447
  filter(!is.na(recode_orient) )## 1441
  

colnames(table1_dat) <- c("id", "condition", "Baseline CDI mean score(0-2)", "3-month CDI mean score", 
"Race", "Age (yrs)", "Biological sex", "Sexual orientation", 
"Language", "Gender identity", "Number of challenges", "Type of challenges", "Type of coping strategies"
)

```
