# Investigate HTE

## Main effect only model

first, replicate the model in the original paper for comparison. the main effect model which adjusted for baseline CDI score is specified as:$$E(Y|\bf{X}) = \text{baseline CDI}+ \text{condition}$$

```{r}
abc_main_dat <- dat_abc %>%  dplyr::select(f1_cdi_mean,condition,b_cdi_mean)

abc_main_m <- lm(f1_cdi_mean~ b_cdi_mean + condition,data=abc_main_dat)

person_main_dat <- dat_person %>%  dplyr::select(f1_cdi_mean,condition,b_cdi_mean)

person_main_m <- lm(f1_cdi_mean~ b_cdi_mean + condition,data=person_main_dat)
```


print the model, compare with the published paper (results are similar):
for project ABC vs control:
```{r}
abc_main_m %>% summary()
tab_model(abc_main_m)
```

for project personality vs control:
```{r}
person_main_m %>% summary()
tab_model(person_main_m)
```

## HTE model

The HTE is defined as:
$$E(Y|\bf{X}) = \text{baseline CDI}+ \text{condition} + \text{lp}+\text{condition}\times \text{lp}$$ where lp is the linear predictor of the baseline model.

```{r}
lp_abc <- predict(abc_base_m, dat_abc)
lp_person <- predict(person_base_m, dat_person)

abc_hte_m <- lm(f1_cdi_mean~ b_cdi_mean + condition*lp_abc,data=dat_abc)
person_hte_m <- lm(f1_cdi_mean~ b_cdi_mean + condition*lp_person,data=dat_person)
```

### HTE Project ABC 
The hte model for Project ABC vs control:
```{r}
summary(abc_hte_m)
tab_model(abc_hte_m)
```

### HTE Project personality 
The hte model for Project personality vs control:
```{r}
summary(person_hte_m)
tab_model(person_hte_m)
```

