# Sensitivity Analysis

##  inverse probability of missingness weighting (IPMW) 
Check the missingness, and regress the missing status on variables with complete info.

```{r}

model_dat <- cope_subset3 %>% 
  dplyr::select(-family_num,-b_response_id,-recode_language,-b_screener_age)
## check missingness
model_dat$missing[complete.cases(model_dat)] <- 0
model_dat$missing[!complete.cases(model_dat)] <- 1

model_dat$missing %>% table()
str(model_dat)

missed <- glm(missing ~ genderid3+b_cdi_mean+family_cat+cope3,
              data = model_dat, family = "binomial")

model_dat$fitted = missed$fitted.values
model_dat$IPCW = (1-mean(model_dat$missing))/(1-model_dat$fitted)
model_dat <- subset(model_dat, complete.cases(model_dat))

```
A summary of the IPCW model:
```{r}
summary(missed)


```
Summary of IPCW weights:
```{r}

summary(model_dat$IPCW)

```

## Baseline prediction models
```{r message=FALSE, warning=FALSE}

ipcw_abc_dat <- model_dat %>% filter(condition!="Project Personality") %>%## ABC vs control
  mutate(condition = as.character(condition),
         condition = as.factor(condition)
  )%>% dplyr::select(-condition,-b_cdi_mean,-fitted,-IPCW)


ipcw_person_dat <- model_dat %>% 
filter(condition!="Project ABC") %>%  ## Personality vs control
 mutate(condition = as.character(condition),
        condition = as.factor(condition)
        )%>% dplyr::select(-condition,-b_cdi_mean,-fitted,-IPCW)


abc_weight <- ipcw_abc_dat$IPCW
person_weight <- ipcw_person_dat$IPCW

abc_ipcw_base_m <- glm(f1_cdi_mean ~., 
             family =gaussian(link="identity"),
             weights =abc_weight,
             data = ipcw_abc_dat)


person_ipcw_base_m <- glm(f1_cdi_mean ~., 
             family =gaussian(link="identity"),
             weights =person_weight,
             data = ipcw_person_dat)
## baseline linear pred values

abc_ipcw_lp <- predict(abc_ipcw_base_m, newdata = ipcw_abc_dat)

person_ipcw_lp <- predict(person_ipcw_base_m, newdata = ipcw_person_dat)
lp_abc <- abc_ipcw_lp
lp_person <- person_ipcw_lp



```
baseline model for Project ABC:
```{r}
tab_model(abc_ipcw_base_m)
```
baseline model for Project personality:
```{r}
tab_model(person_ipcw_base_m)
```

## Main effect model

```{r}

ipcw_abc_dat <- model_dat %>% filter(condition!="Project Personality") %>%## ABC vs control
  mutate(condition = as.character(condition),
         condition = as.factor(condition)
  )%>% dplyr::select(-fitted,-IPCW)


ipcw_person_dat <- model_dat %>% 
filter(condition!="Project ABC") %>%  ## Personality vs control
 mutate(condition = as.character(condition),
        condition = as.factor(condition)
        )%>% dplyr::select(-fitted,-IPCW)



abc_ipcw_main_m <- glm(f1_cdi_mean ~ b_cdi_mean + condition, 
             family =gaussian(link="identity"),
             weights =abc_weight,
             data = ipcw_abc_dat)



person_ipcw_main_m <- glm(f1_cdi_mean ~b_cdi_mean + condition , 
             family =gaussian(link="identity"),
             weights =person_weight,
             data = ipcw_person_dat)



```
Main effect model for Project ABC:
```{r}
tab_model(abc_ipcw_main_m)


```
Main effect model for Project Personality:
```{r}
tab_model(person_ipcw_main_m)
```

## The HTE models

```{r}


abc_ipcw_hte_m <- glm(f1_cdi_mean ~b_cdi_mean + condition * abc_ipcw_lp, 
             family =gaussian(link="identity"),
             weights =abc_weight,
             data = ipcw_abc_dat)



person_ipcw_hte_m <- glm(f1_cdi_mean ~b_cdi_mean + condition * person_ipcw_lp, 
             family =gaussian(link="identity"),
             weights =person_weight,
             data = ipcw_person_dat)





```

HTE model for Project ABC:
```{r}
tab_model(abc_ipcw_hte_m)

```
HTE model for Project Personality:
```{r}
tab_model(person_ipcw_hte_m)
```


```{r}
## rename variabels 

abc_main_m <- abc_ipcw_main_m

person_main_m <- person_ipcw_main_m

abc_hte_m <- abc_ipcw_hte_m
  
person_hte_m <- person_ipcw_hte_m
  
  

## cATE/HTE
## project ABC vs control
hte_dat <- ipcw_abc_dat

hte_dat$condition = 'Placebo Control'
abc_hte_ctrl <- predict(abc_hte_m,hte_dat)

hte_dat$condition  = 'Project ABC'
abc_hte_trt <- predict(abc_hte_m,hte_dat)

abc_hte <- abc_hte_trt-abc_hte_ctrl

## hte personality vs control
hte_dat <- ipcw_person_dat

hte_dat$condition = 'Placebo Control'
person_hte_ctrl <- predict(person_hte_m,hte_dat)

hte_dat$condition  = 'Project Personality'
person_hte_trt <- predict(person_hte_m,hte_dat)
person_hte <- person_hte_trt-person_hte_ctrl


point_df <- data.frame(Comparsion= c("Project ABC vs Control","Project personality vs Control" ),
                       ATE = c(abc_ate,person_ate),
                       SE = c(summary(abc_main_m)$coefficients[, "Std. Error"][3],
                              summary(person_main_m)$coefficients[, "Std. Error"][3])
                       )

kable(point_df, caption = "summary of avearged treatment effect")

```

## Risk stratification

```{r}
## calibration plot

abc_ate <- coef(abc_main_m)[3]
person_ate <- coef(person_main_m)[3]


person_cal_dat <- data.frame(person_ate,
                          person_hte,
                          lp_person)

person_cal_dat$quantile_grp <- cut(person_cal_dat$lp_person,
                               breaks = quantile(person_cal_dat$lp_person, probs = seq(0, 1, by = 0.2)),
                               include.lowest = TRUE,
                               labels = FALSE)

## compute the averaged hte effect in each quantile risk grp
person_avg_hte <- person_cal_dat %>%
  group_by(quantile_grp) %>%
  summarise(person_avg_hte = mean(person_hte, na.rm = TRUE))

```

## Boot CI

```{r message=FALSE, warning=FALSE}
## for ipcw data
## ipcw_person_dat
boot2_f <- function(mydat=NULL,seed=1017){
  set.seed(seed)
  abc_boot_res <- NULL
  for (i in 1:1000){
    boot.idx <- sample(1:dim(mydat)[1], size = dim(mydat)[1], replace = T)
    boot.data <- mydat[boot.idx,]
    
    abc_main_dat <- boot.data %>%  dplyr::select(f1_cdi_mean,condition,b_cdi_mean)
    
    abc_main_m <- lm(f1_cdi_mean~ b_cdi_mean + condition,data=abc_main_dat)
    
    lp_abc <- predict(abc_main_m,boot.data)
    
    abc_ate <- coef(abc_main_m)[3]
    
    abc_hte_m <- glm(f1_cdi_mean ~b_cdi_mean + condition*lp_abc, 
             family =gaussian(link="identity"),
             weights =boot.data$IPCW,
             data = boot.data)
    
    ## cATE/HTE
    ## project ABC vs control
    hte_dat <- boot.data
    
    trt_levels <- unique(boot.data$condition) %>% as.character()
    
    trt <- trt_levels[!(trt_levels %in% 'Placebo Control')]
    
    hte_dat$condition = 'Placebo Control'
    abc_hte_ctrl <- predict(abc_hte_m,hte_dat)
    
    hte_dat$condition  = trt 
    abc_hte_trt <- predict(abc_hte_m,hte_dat)
    
    abc_hte <- abc_hte_trt-abc_hte_ctrl
    
    
    
    ## calibration plot
    abc_cal_dat <- data.frame(abc_ate,
                              abc_hte,
                              lp_abc)
    
    abc_cal_dat$quantile_grp <- cut(abc_cal_dat$lp_abc,
                                    breaks = quantile(abc_cal_dat$lp_abc, probs = seq(0, 1, by = 0.2)),
                                    include.lowest = TRUE,
                                    labels = FALSE)
    
    ## compute the averaged hte effect in each quantile risk grp
    avg_hte <- abc_cal_dat %>%
      group_by(quantile_grp) %>%
      summarise(avg_hte = mean(abc_hte, na.rm = TRUE))
    
    abc_boot_res <- rbind(abc_boot_res,avg_hte)
  }
  return(abc_boot_res)
}
```

For Project ABC:
```{r message=FALSE, warning=FALSE}
## compute bootstrapped CI
abc_boot_res <- boot2_f(mydat = ipcw_abc_dat)
abc_boot_cali_ci <- abc_boot_res %>%
  group_by(quantile_grp) %>%
  summarise(
    lower_quantile = round(quantile(avg_hte, probs = 0.025), 4),
    upper_quantile = round(quantile(avg_hte, probs = 0.975), 4)
  )
abc_cali_result <- left_join(abc_avg_hte,abc_boot_cali_ci)
```


For Project personality:
```{r}
person_boot_res <- boot2_f(mydat = dat_person)

person_boot_cali_ci <- person_boot_res %>%
  group_by(quantile_grp) %>%
  summarise(
    lower_quantile = round(quantile(avg_hte, probs = 0.025), 4),
    upper_quantile = round(quantile(avg_hte, probs = 0.975), 4)
  )


person_cali_result <- left_join(person_avg_hte,person_boot_cali_ci)

## identify the bounds for cali plots

max_cali_y <- max(abc_cali_result$upper_quantile,person_cali_result$upper_quantile) 

min_cali_y <- min(abc_cali_result$lower_quantile,person_cali_result$lower_quantile) 

## check if the ylims are correct 
### I used -0.2 and 0.5 range for the y axis in the calibration plots

logic1 <- min_cali_y <=  0.05 & min_cali_y >=-0.2

logic2 <- max_cali_y <=  0.05 & max_cali_y >=-0.2

if(!logic1 & ! logic2){
  print(paste0("please make sure the range of y axis in the following calibration plot is [", min_cali_y, ",",max_cali_y,']'))
}else{logic_3 = logic1+logic2}
```
## Risk stratification 
```{r}
abc_cali_plot <- ggplot(abc_cali_result, aes(x = as.factor(quantile_grp), y = abc_avg_hte)) +
  geom_point(size = 2.5,color = "#8B0000") +
  # geom_line(aes(group = 1), color = "blue") +
  geom_errorbar(aes(ymin = lower_quantile, ymax = upper_quantile), width = 0.05, color = "#8B0000") +
  labs(x = "",
       y = "Mean heter_mean_diff"
       # title = ""
  ) +
  geom_hline(yintercept = abc_ate, linetype = "dashed", color = "grey")+
  theme_minimal()+
  scale_y_continuous(
    limits = c(-0.2, 0.05), 
    breaks = seq(-0.2, 0.05, by = 0.05)
  )+
 # ylim(c(min_cali_y,max_cali_y))+
  ylab("Mean difference")+
  # ylab(expression(atop("Risk Difference, %", atop("Harm" %<-% phantom("     ") %->% "Benefit")))) +  # Custom y-axis label
  theme(axis.title.y = element_text(angle = 90, vjust = 0.5, size = 14))
```

```{r}
abc_lp_plot <- ggplot(abc_cal_dat, aes(x = lp_abc)) +
  geom_histogram(binwidth = 0.02, fill = "#8B0000") +
  labs(x = "Predicted CDI mean score using baseline covariates (Project ABC)", y = NULL) +
  theme_minimal()

abc_combo_plot <- cowplot::plot_grid(
  abc_cali_plot,
  abc_lp_plot,
  ncol = 1,
  align = "v",
  rel_heights = c(3, 1)  
)



# Display the combined plot
abc_combo_plot
abc_cal_dat$lp_abc %>% summary()
```
```{r}
person_cali_plot <- ggplot(person_cali_result, aes(x = as.factor(quantile_grp), y = person_avg_hte)) +
  geom_point(size = 2.5, color = "#8B0000") +
  # geom_line(aes(group = 1), color = "blue") +
  geom_errorbar(aes(ymin = lower_quantile, ymax = upper_quantile), width = 0.05, color = "#8B0000") +
  labs(x = "",
       y = "Mean heter_mean_diff"
       # title = ""
       ) +
  geom_hline(yintercept = person_ate, linetype = "dashed", color = "grey")+
  theme_minimal()+
  scale_y_continuous(
    limits = c(-0.2, 0.05), 
    breaks = seq(-0.2, 0.05, by = 0.05)
  )+
  ylab("Mean difference")+
 # ylab(expression(atop("Risk Difference, %", atop("Harm" %<-% phantom("     ") %->% "Benefit")))) +  # Custom y-axis label
  theme(axis.title.y = element_text(angle = 90, vjust = 0.5, size = 14))
```

```{r}
person_lp_plot <- ggplot(person_cal_dat, aes(x = lp_person)) +
  geom_histogram(binwidth = 0.01, fill = "#8B0000") +
  labs(x = "Predicted CDI mean score using baseline covariates(Project Personality)", y = NULL) +
  theme_minimal()

person_combo_plot <- cowplot::plot_grid(
  person_cali_plot,
  person_lp_plot,
  ncol = 1,
  align = "v",
  rel_heights = c(3, 1)  
)

person_combo_plot
```

```{r}
cal_plots <- ggarrange(abc_combo_plot, person_combo_plot, ncol = 2, nrow = 1)
cal_plots

ggsave("figures/cal_plots_ipcw.png", width = 10, height = 7, dpi = 600)
```

Distribution of baseline depression severity score
```{r}
abc_cal_dat_report <- abc_cal_dat

person_cal_dat_report <- person_cal_dat


abc_cal_dat_report$grp ="Project ABC"

person_cal_dat_report$grp = "Project Personality"

colnames(person_cal_dat_report) = colnames(abc_cal_dat_report)

combined_cal_dat_report<- rbind(abc_cal_dat_report,person_cal_dat_report)


combined_hist_plot <-ggplot(combined_cal_dat_report, aes(x = lp_abc, fill = grp)) +
  geom_histogram(binwidth = 0.03, alpha = 0.8, position = "identity") +
  labs(x = "Predicted 3-month CDI-SF mean score using baseline prediction models", y = "Frequency", fill = "Project") +
  theme_minimal() +
  scale_fill_manual(values = c("Project ABC" = "#1f78b4", "Project Personality" = "#8B0000"))

combined_hist_plot
ggsave("figures/combined_hist_plot_ipcw.png", width = 10, height = 7, dpi = 600)
```

